### 2016-06-07 conclusion.tex
more fixes to address Jim's comments
- mention FP and partitioning early on
- spell out small numbers

Also add acknowledgements.
shorten acknowledgement
ack
add ack sfb876
snapshot editing (not yet finished with section 4)
add remarks on DPCP/DFLP and some minor edits

Furthermore, the original proposal \cite{Raj:suspension1991} left open the question of how to convert a segmented self-suspending task set to a corresponding set of deferrable tasks. Taking into account recent developments~\cite{ecrts15nelissen}, we have observed that such a task set transformation is non-trivial in the general case.

@@

>>>>

The original proposal \cite{Raj:suspension1991} further left open the question of how to convert a segmented self-suspending task set to a corresponding set of deferrable tasks. Taking into account recent developments~\cite{ecrts15nelissen}, we have observed that such a transformation is non-trivial in the general case.

@@

\section*{Acknowledgements}

We thank James H.\ Anderson and Raj Rajkumar for their comments on early drafts of this paper.
This work has been supported by DFG, as part of the Collaborative
Research Center SFB876. % (\url{http://sfb876.tu-dortmund.de/}).

### 2016-06-07 locking.tex
add remarks on DPCP/DFLP and some minor edits

\subsection{Case 1: Locking Takes Effect at Earliest Segment Eligibility Time}
In the following example, we assume the first interpretation, i.e., that the processing of lock requests is delayed until the point when a resuming segment would no longer be subject to any delay due to period enforcement. We show that this interpretation leads to a deadline miss in a task set that would otherwise be trivially schedulable.

@@

\subsection{Case 2: Locking Takes Effect Immediately}
 From now on, we assume the second interpretation: all lock requests are processed immediately when they are made, even if this causes the shared resource to be locked by a task that is not yet eligible to execute according to  the rules of the period enforcer algorithm. We construct an example in which a task's response time grows with each job until a deadline is missed.

@@

>>>>

\subsection{Case 1: Locking Takes Effect at Earliest Segment Eligibility Time}
\label{sec:sem-case-1}
In the following example, we assume the first interpretation, i.e., that the processing of lock requests is delayed until the point when a resuming segment would no longer be subject to any delay due to period enforcement. We show that this interpretation leads to a deadline miss in a task set that would otherwise be trivially schedulable.

@@

\subsection{Case 2: Locking Takes Effect Immediately}
\label{sec:sem-case-2}
 From now on, we assume the second interpretation: all lock requests are processed immediately when they are made, even if this causes the shared resource to be locked by a task that is not yet eligible to execute according to  the rules of the period enforcer algorithm. We construct an example in which a task's response time grows with each job until a deadline is missed.

@@

Notably, the examples in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} assume a shared-memory locking protocol: once a lock is granted, tasks execute their own critical sections, on their assigned processors. One may wonder whether  effects similar to those described in in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2} can also occur under \emph{distributed} real-time locking protocols such as the DPCP~\cite{RSL:88} or the DFLP~\cite{Br:13,Br:14}, where critical sections may be executed on dedicated \emph{synchronization processors}. In this case, the self-suspension occurs on the task's \emph{application processor}, which is different from the (remote) synchronization processor on which the critical section is executed. This separation allows employing period enforcement  only on application processors (while avoiding it on synchronization processors) without incurring the feedback cycle between blocking times and self-suspension times highlighted in Sections~\ref{sec:sem-case-1} and~\ref{sec:sem-case-2}. However, period enforcement still invalidates all existing blocking analyses for distributed real-time semaphore protocols~\cite{RSL:88,Raj:91,Br:13} because it artificially increases blocking times if tasks contain multiple accesses to shared resources.

### 2016-06-07 untitled.tex
add remarks on DPCP/DFLP and some minor edits

On uniprocessors, this relaxation does not introduce additional pessimism: since any two jobs of a sporadic task $\tau_i$ are  known to be released \emph{at least} $T_i$ time units apart, the sporadic task model~\cite{Mo:83} still allows for schedulability analysis that is as accurate as Liu and Layland's analysis of periodic tasks~\cite{LL:73}.

@@

\begin{enumerate}
\setcounter{enumi}{2}
	\item The period enforcer algorithm invalidates all existing blocking analyses for shared-memory real-time semaphore protocols as there exist non-trivial feedback cycles between the period enforcer rules and blocking durations.
\end{enumerate}

>>>>

On uniprocessors, the relaxation from periodic to sporadic job arrivals does not introduce additional pessimism:\footnote{Assuming that all periodic tasks release a job synchronously at time zero.} since any two jobs of a sporadic task $\tau_i$ are  known to be released \emph{at least} $T_i$ time units apart, the sporadic task model~\cite{Mo:83} still allows for schedulability analysis that is as accurate as Liu and Layland's analysis of periodic tasks~\cite{LL:73}.

@@

\begin{enumerate}
\setcounter{enumi}{2}
	\item The period enforcer algorithm invalidates all existing blocking analyses for real-time semaphore protocols as there exist non-trivial feedback cycles between the period enforcer rules and blocking durations.
\end{enumerate}
